Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-03-09 size_differentiated_export.tex
Updates from Overleaf

%FIG8
 \begin{figure}[ht!]
	\centering
	\includegraphics[width = .65\linewidth]{figures/cartoon_meso}\\[.2cm]
	\includegraphics[width = .65\linewidth]{figures/cartoon_submeso}
	\caption{Schematics showing the respective contribution to export of particles with different sinking velocities in (top) a gravitationally-driven system (i.e., weak submesoscale dynamics), and (bottom) an advectively-driven system (i.e., strong submesoscale dynamics).}
	\label{fig: export_cartoon}
\end{figure}

In a system affected by submesoscale dynamics, localized strong downwelling vertical currents are generated. This effectively shortens the export timescale of slower-sinking particles, entering a regime where export timescales are shorter than remineralization timescales (Figure \ref{fig: export_cartoon}b). In this regime, slower-sinking particles significantly contribute to POC export. \fixme{In this study, sinking-velocity classes that did not contribute to POC export in a mesoscale regime, are found to contribute up to 30\% of POC export in the most extreme case, where $\xi =4$ Also talk about te fct that it is what we see in Fig 8 with the reveral fo the order.} %Implementing remineralization process has little to no impact on the respective contributions of the different sinking-velocity classes as the impact of remineralization is smaller when export flux is advectively-driven, as opposed to gravitationally-driven.

\section{Conclusion}
\label{sec: Conclusions}
The main conclusions of this study are: 
\begin{enumerate}
\item Submesoscale activity at station Papa is enhanced in the wintertime, leading to larger vertical velocities than in the summertime. The export mechanism in the winter is thus driven by advective sinking, as opposed to gravitational sinking in the summertime.
\item Submesoscale dynamics generally enhance export by increasing the contribution of slower-sinking particles to POC export by increasing the number of particle exported through advective sinking. The contribution of slower-sinking particles in ageostrophic flows is at least significant, and can be dominant in specific conditions.
\item Contribution of slower-sinking particles to POC export depends on the slope of the particle size spectra (i.e., Junge Slope), that controls the relative number of particles per size class. Three cases emerge in this study:
\begin{enumerate}
	\item If the Junge slope is smaller than 3, larger particles contribute most to export independently of flow dynamics, as there are no mechanism capable of selectively exporting slower-sinking particles.
	\item If the Junge slope equals 3, the respective contributions of the different size classes depend on the dynamical characteristics of the flow, as it influences the number of particles being exported. If 100\% of the particles is exported in all sinking classes, then each class contributes equally to POC export.
	\item If the Junge slope is greater than 3, ocean dynamics become the determining factor on which classes dominate: in a mostly geostrophic flow with weak vertical velocities, an intermediate sinking-velocity class will dominate POC export. In a flow with ageostrophic circulation leading to larger vertical velocities, slower sinking classes can potentially dominate export.
	\end{enumerate}
\item Remineralization processes reduce the contribution of slower-sinking particles when export dynamics are dominated by gravitational sinking (i.e., in a geostrophic flow). As flow dynamics become ageostrophic, advective sinking leads the export and remineralization processes have a limited impact.
%\item[(5)] Under specific conditions (large Junge slope and strongly ageostrophic flow), remineralization processes counter-intuitively enhance the role of slower-sinking (and non-sinking) particles to the point where export is dominated by these slow-sinking particles, therefore challenging the traditional paradigm of carbon export.
\end{enumerate}

>>>>

%FIG9
 \begin{figure}[ht!]
	\centering
	\includegraphics[width = .65\linewidth]{figures/Fig9_cartoon_meso}\\[.2cm]
	\includegraphics[width = .65\linewidth]{figures/Fig9_cartoon_submeso}
	\caption{Schematics illustrating the respective contribution to export of particles with different sinking velocities for $\xi > 3$ in (a) a gravitationally-driven system (i.e., weak submesoscale dynamics), and (b) an advectively-driven system (i.e., strong submesoscale dynamics).}
	\label{fig: export_cartoon}
\end{figure}

In a system affected by submesoscale dynamics, localized strong downwelling vertical currents are generated. This effectively shortens the export timescale of slower-sinking particles, entering a regime where export timescales are shorter than remineralization timescales (Figure \ref{fig: export_cartoon}b). In this regime, slower-sinking particles significantly contribute to POC export, and can even dominate the export signal for large $\xi$. This scenario is captured in one of the Lagrangian experiment and shown in Figure \ref{fig: biomass_export}b, where the contribution to biomass export from the 0.025 m/day sinking class exceeds the one from the 0.5 m/day sinking class. This surprising result further emphasizes the key role played by slow-sinking particles in POC export, especially in the presence of submesoscale dynamics and large $\xi$.

\section{Conclusion}
\label{sec: Conclusions}
The main conclusions of this study are: 
\begin{enumerate}
\item Ocean dynamics in the subpolar Pacific northeast exhibit a seasonal cycle with low submesoscale activity in the summertime, and more submesoscale features in the wintertime. Submesoscale dynamics generate larger, and asymmetrical, vertical currents leading to an export mechanisms dominated by advective processes, as opposed to gravitationally-driven in the summertime.

\item Submesoscale dynamics generally enhance export by increasing the contribution of slower-sinking particles to POC export by increasing the number of particle exported through advective sinking. The contribution of slower-sinking particles subducted through irreversible ageostrophic processes to particle export is at least significant, and can be dominant in specific conditions.
\item Contribution of slower-sinking particles to POC export depends on the slope of the particle size spectra (i.e., Junge Slope), that controls the relative number of particles per size class. Three cases emerge in this study:
\begin{enumerate}
	\item If the Junge slope is smaller than 3, larger particles contribute most to export independently of flow dynamics, as there are no mechanism capable of selectively exporting slower-sinking particles.
	\item If the Junge slope equals 3, the respective contributions of the different size classes depend on the dynamical characteristics of the flow, as it influences the number of particles being exported. If 100\% of particles is exported in all sinking classes, then each class contributes equally to POC export.
	\item If the Junge slope is greater than 3, as most commonly observed, ocean dynamics become the determining factor on which classes dominate: in a mostly geostrophic flow with weak vertical velocities, an intermediate sinking-velocity class will dominate POC export. In a flow with ageostrophic circulation leading to larger vertical velocities, slower sinking classes can potentially dominate export.
	\end{enumerate}
\item Remineralization processes reduce the contribution of slower-sinking particles when export dynamics are dominated by gravitational sinking (i.e., in a geostrophic flow). As flow dynamics become ageostrophic, advective sinking leads the export and remineralization processes have a limited impact.
\end{enumerate}
